Subset occurrence data to IUCN Tropical Andes Lowland and Montane Forest

### 2023-08-03 code/L1/L1_TropicalAndes_subset_occ_forest.Rmd
fix code converting to SpatialPointsDataframe change plant_occ name fix issue with removing NAs

```{r}
TropicalAndes_IUCNHabitat_Forest0.5 <- aggregate(TropicalAndes_IUCNHabitat_Forest, 50, fun=mean, na.rm=TRUE)
TropicalAndes_IUCNHabitat_Forest0.5
```

# Rasterize occurrence data
```{r}
# convert to SpatialPointsDataFrame
coordinates(TropicalAndes_GBIF_plant_occ_cleaned) <- ~ decimalLatitude + decimalLongitude
coordinates(TropicalAndes_frugivore_occ) <- ~ decimalLatitude + decimalLongitude
TropicalAndes_GBIF_plant_occ_cleaned
TropicalAndes_frugivore_occ
```

# Crop occurrence data to forest extent
```{r}
TropicalAndes_GBIF_plant_occ_cleaned$ref<- extract(TropicalAndes_IUCNHabitat_Forest, TropicalAndes_GBIF_plant_occ_cleaned)
TropicalAndes_frugivore_occ$ref<- extract(TropicalAndes_IUCNHabitat_Forest, TropicalAndes_frugivore_occ)
```

```{r}
TropicalAndes_GBIF_plant_occ_cleaned$ref <- as.character(TropicalAndes_GBIF_plant_occ_cleaned$ref)
TropicalAndes_frugivore_occ$ref <- as.character(TropicalAndes_frugivore_occ$ref)
```

```{r}
plant_occ_forest <- TropicalAndes_GBIF_plant_occ_cleaned@data
frugivore_occ_forest <- TropicalAndes_frugivore_occ@data
```

```{r}
#remove row if ref = NA
plant_occ_forest <- plant_occ_forest[plant_occ_forest$ref != "NA", ]
frugivore_occ_forest <- frugivore_occ_forest[frugivore_occ_forest$ref != "NA", ]
```

>>>>

```{r}
TropicalAndes_IUCNHabitat_Forest0.3 <- aggregate(TropicalAndes_IUCNHabitat_Forest, 30, fun=mean, na.rm=TRUE)
TropicalAndes_IUCNHabitat_Forest0.3
```

# Rasterize occurrence data
```{r}
# convert to SpatialPointsDataFrame
coordinates(TropicalAndes_plant_occ) <- ~ decimalLongitude + decimalLatitude
coordinates(TropicalAndes_frugivore_occ) <- ~ decimalLongitude + decimalLatitude
proj4string(TropicalAndes_plant_occ) <- CRS("+proj=longlat +datum=WGS84 +no_defs")
proj4string(TropicalAndes_frugivore_occ) <- CRS("+proj=longlat +datum=WGS84 +no_defs")
TropicalAndes_plant_occ
TropicalAndes_frugivore_occ
```

# Crop occurrence data to forest extent
```{r}
TropicalAndes_plant_occ$ref<- extract(TropicalAndes_IUCNHabitat_Forest, TropicalAndes_plant_occ)
TropicalAndes_frugivore_occ$ref<- extract(TropicalAndes_IUCNHabitat_Forest, TropicalAndes_frugivore_occ)
```

```{r}
TropicalAndes_plant_occ$ref <- as.character(TropicalAndes_plant_occ$ref)
TropicalAndes_frugivore_occ$ref <- as.character(TropicalAndes_frugivore_occ$ref)
```

```{r}
plant_occ_forest <- TropicalAndes_plant_occ@data
frugivore_occ_forest <- TropicalAndes_frugivore_occ@data
```

```{r}
#remove row if ref = NA
plant_occ_forest <- plant_occ_forest[!is.na(plant_occ_forest$ref), ]
frugivore_occ_forest <- frugivore_occ_forest[!is.na(frugivore_occ_forest$ref), ]
```
